Noisy Work: A Review of The Uncertainty Visualisation Literature

### 2024-02-16 paper.qmd
added summary paper

>>>>

@Griethe2006 provided a summary of the uncertainty visualisation literature and did not take any particular angle in the analysis. She makes the point that there is no universally accepted definition of uncertainty and no unicersally accepted way to display it. She defined uncertainty as "the degree to which the lack of knowledge about the amount of error is responsible for hesitancy in accepting results and observations without caution". She then explains that there are two ways to visualise uncertianty, implicitly and explicitly. When a visualisaion is implicit, the uncertainty is considered an uninteresting feature of the data, and instead of mapping some quantification of uncertainty to a visual feature, data is filtered out if it does not meet a specified "certainty" threshold. These statements clearly points towards a signal/noise dichotomy with normal visualisation and uncertainty visualisation. Additionally she notes that the motivation of the analysis is important, by stating "one has to answer the questions which kinds of uncertainty are relevant from the data’s perspective, which kinds are helpful from the perspective of the visualization steps and which kinds are practicably extractable from the perspective of the available methods?", and "The decision of which of these techniques to choose strongly depends on the intended goal" when commenting on which uncertainty visualisation techniques should be used. She clearly sees uncertainty as additional information or data, and therefore sees the uncertainty visualisation problem as a specific case of the high dimensional visualisation issues. She mentions that there are detailled classifications of uncertainty but the literature and subsequent techniques are not ballanced, and instead concentrate on scalar values. In facing this lack of ballance she creates a new classification system for uncertainty visualisation. She commented that uncertainty appears at every step in the analyis pipeline, and commented on some the mathematical definitions that seek to quantify uncertianty, but did not explain how these mathematical definitions can be combined across levels. Unfortunately this quantification is needed since she mentioned that in order to visualise uncertainty, it needs to be measurable.
